An Open System for\\ Managing Short Programming Exercises

### 2013-08-08 paper/talk.tex
a couple more small tweaks

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum material
        depends on how many students can access it
  \item Systematically eliminating barriers to adoption and distribution maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier
    \item Restrictive licenses are a barrier
    \item Control by a central authority is a barrier
  \end{itemize}
  \item Ideal situation: resources are available to {\bf anyone} at {\bf any time} for {\bf any purpose}
%  \item Case in point...
\end{itemize}

@@

\begin{itemize}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to work: 60+ concurrent users with modest hardware
    \item Load testing: with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions requires significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
  \item {\bf We can host CloudCoder for your course!}
    \begin{itemize}
    \item We have a grant from Amazon to cover hosting costs for
          a small number of institutions/courses
    \item {\bf Talk to us if you are interested!}
    \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item The impact of a pedagogical technique or curriculum resource
        depends on how many students can access it
  \item Systematically eliminating barriers to adoption and distribution maximizes impact
  \begin{itemize}
    \item Requiring payment is a barrier
    \item Restrictive licenses are a barrier
    \item Control by a central authority is a barrier
  \end{itemize}
  \item Ideal situation: resources are available to {\bf anyone} at {\bf any time} for {\bf any purpose}
%  \item Case in point...
\end{itemize}

@@

\begin{itemize}
  \item Requires two Linux servers to host (one network-facing)
    \begin{itemize}
    \item Relatively easy to install
    \item Known to work: 60+ concurrent users with modest hardware
    \item Load testing: with 700+ concurrent users
          on moderate server hardware
      \begin{itemize}
      \item Compiling and testing submissions can require significant
            CPU resources, but is easy to scale up by adding more
            build servers
      \end{itemize}
    \item Cost to host per course-semester: perhaps \$1-\$3 per student
          (e.g., using Amazon EC2)
    \end{itemize}
  \item {\bf We can host CloudCoder for your course!}
    \begin{itemize}
    \item We have a grant from Amazon to cover hosting costs for
          a small number of institutions/courses
    \item {\bf Talk to us if you are interested!}
    \end{itemize}
\end{itemize}
